Statistical Modeling of Galaxy Catalogues with Normalizing Flows

### 2022-05-25 src/tex/ms.tex
Added two_moons figure script. Added pre-commits.

@@

\note{Two moons example figure. Need to convert this to a uniform distribution.}

@@

\note{
Discuss latent distributions here.
Note that most applications use a Normal Distribution, but since the splines have a compact domain, we need to choose a latent distribution with compact support, or else we might generate strange outliers when sampling from the flow.

Some text for this might already be in the creation module draft.
}

@@

We trained the normalizing flow for \note{N} epochs using the Adam optimizer \citep{adam} with a learning rate of \note{N} to minimize the negative log likelihood, 
\begin{align}
    \mathcal{L} = \mathbb{E}[p(x)],
\end{align}
where the expectation is performed over galaxies in the training set and $p(x)$ is defined in Equation \ref{eq:px}.
Training took \note{N} minutes on a Tesla P100 12GB GPU.
The training and test losses can be seen in Figure \note{X}.

>>>>

\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{shapes}
\usetikzlibrary{fit}

\newcommand{\comment}[1]{}

@@

\note{Two moons example figure. Need to convert this to a uniform distribution.}
\begin{figure}[ht!]
    \script{two_moons_example.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/twomoons_example.pdf}
        \caption{
            Need to write!
        }
        \label{fig:two-moons}
    \end{centering}
\end{figure}

@@

\note{
Discuss latent distributions here.
Note that most applications use a Normal Distribution, but since the splines have a compact domain, we need to choose a latent distribution with compact support, or else we might generate strange outliers when sampling from the flow.
Some text for this might already be in the creation module draft.
}

@@

We trained the normalizing flow for \note{N} epochs using the Adam optimizer \citep{adam} with a learning rate of \note{N} to minimize the negative log-likelihood,
\begin{align}
    \mathcal{L} = - \, \mathbb{E}[ \, \log p(x) \, ],
\end{align}
where the expectation is performed over galaxies in the training set and $p(x)$ is defined in Equation \ref{eq:px}.
Training took \note{N} minutes on a Tesla P100 12GB GPU.
The training and test losses can be seen in Figure \note{X}.
